%!TEX root = main.tex

\section{Conclusion}
\label{sec:conclude}

%long version
Mobile voice search session consists of a voice recognition phase for voice data uploading and a subsequent web search phase for search with recognized words. Analyzing the TCP performance of mobile voice search at server side can shed useful lights on the understanding of TCP short flows for both upload and download. By observing  a unique dataset collected from a voice search service, we find a considerable fraction of outliers that suffer from very long finish time in both phases, which motivates us to perform a detailed analysis on the TCP performance and its causes. We focus on the disparity that might exist between TCP upload and download flows and also the possible difference when searching using 3G and WiFi connection. We observed a better performance of 3G flows than WiFi flows for mobile voice search due to higher packet loss rate and longer RTT in WiFi network. In fact, WiFi flows are more likely to use timeout retransmission for packet loss recovery. Timeout retransmission will dominate the finish time once it happens. RTT on the other hand plays an important role when no packet is lost. We also classified the timeout retransmissions and found the different compositions of timeout retransmissions between WiFi flows and 3G flows. These observations constitute valuable insights for improving the user-perceived performance in voice search service.

%short version
%Mobile voice search session consists of a voice recognition phase for voice data uploading and a subsequent web search phase for search with recognized words. Analyzing the TCP performance of mobile voice search at server side can shed useful lights on the understanding of TCP short flows for both upload and download. By observing  a unique dataset collected from a voice search service, we find a considerable fraction of outliers that suffer from very long finish time in both phases, which motivates us to perform a detailed analysis on the TCP performance and its causes. We focus on the disparity that might exist between TCP upload and download flows and also the possible difference when searching using 3G and WiFi connection. In particular, we analyzed timeout retransmission, an expensive operation for packet loss recovery as it dominates the finish time once it happens. We have made several key observations , which constitute valuable insights for improving the user-perceived performance in voice search service.
